---
title: "Association of Health Outcomes with Type of Health Insurance Coverage: An Instrumental Variable Analysis"
author: "Kay Royo"
date: "`r format(Sys.time(), '%Y %B %d')`"
output:  
  rmdformats::robobook:
    self_contained: true
    fig_caption: true
---

```{r setup, include=FALSE}
# SET CHUNK OPTIONS 
knitr::opts_chunk$set(echo = TRUE, comment = NA, warning = FALSE, message = FALSE) 
# CLEAR COMPUTE MEMORY
rm(list=ls())
```

# I. Data Preprocessing 


```{r, echo=FALSE, message=FALSE, warning=FALSE}
# LOAD SAS DATA
library(haven)
health <- read_sas("C:/Users/kayan/UCD/STA250/Final_Project/Data/Health/ADULT_SAS_PUF_2021/SAS/adult.sas7bdat")
```

```{r,  echo=FALSE,message=FALSE, warning=FALSE}
# REMOVE NO INSURANCE RECORDS 
health <- health[!health$INSTYPE == "1",] #1=uninsured
```

```{r,  echo=FALSE,message=FALSE, warning=FALSE}
# EXCLUDE PREGRNANT WOMEN RECORDS 
health <- health[!health$AD13 == "Yes",] 
```

```{r,  echo=FALSE,message=FALSE, warning=FALSE}
# RECODE INSURANCE TYPE: COMMERCIAL & GOVERNMENT-FUNDED INSURANCE 
library(car)
health$INSTYPE <- recode(health$INSTYPE,"c('2','3','4', '5', '9')='Public'") #1
health$INSTYPE <- recode(health$INSTYPE,"c('7','8')='Private'") #0
```

```{r,  echo=FALSE,message=FALSE, warning=FALSE}
# RECODE EMPLOYMENT TYPE: EMPLOYED & NOT EMPLOYED 
health$WRKST_P1 <- recode(health$WRKST_P1,"c('1','2','3')='Employed'")
health$WRKST_P1 <- recode(health$WRKST_P1,"c('4','5')='Unemployed'")
```

```{r,  echo=FALSE,message=FALSE, warning=FALSE}
# RECODE HH TOTAL ANNUAL INCOME BEFORE TAXES
health$AK22_P1 <- recode(health$AK22_P1,"c('2','3', '4')='2'")
health$AK22_P1 <- recode(health$AK22_P1,"c('5','6', '7')='3'")
health$AK22_P1 <- recode(health$AK22_P1,"c('8','9', '10')='4'")
health$AK22_P1 <- recode(health$AK22_P1,"c('11','12', '13')='5'")
health$AK22_P1 <- recode(health$AK22_P1,"c('14','15', '16')='6'")
health$AK22_P1 <- recode(health$AK22_P1,"c('17','18', '19')='7'")
```


```{r,  echo=FALSE,message=FALSE, warning=FALSE}
# SELECT FEATURES
health  <- health[c('BMI_P', 'INSTYPE','OVRWT', 'WRKST_P1','SREDUC','SRAGE_P1', 'CITIZEN2', 'OMBSRR_P1',  'PCTLF_P', 'AK22_P1', 'AB1', 'FAMSIZE2_P1', 'AD65D')]
```


```{r,  echo=FALSE,message=FALSE, warning=FALSE}
# RENAME FEATURES
colnames(health) <- c('bmi', 'insurance','obese','employment','education','age', 'citizenship', 'race', 'percent_life_US', 'hhtotal_income', 'gen_health_cond', 'family_size', 'gender')
```

```{r,  echo=FALSE,message=FALSE, warning=FALSE}
# CHANGE VARIABLE TYPES 
names = c('insurance','obese','employment','education','citizenship', 'race',  'percent_life_US', 'hhtotal_income', 'gen_health_cond', 'family_size', 'gender')
health[,names] <- lapply(health[,names] , factor)
names = c('bmi', 'age')
health[,names] <- lapply(health[,names] , as.numeric)
```

```{r, echo = FALSE,  fig.align = 'left', fig.cap = 'Figure 11: Box-Cox Plot',message=FALSE, warning=FALSE}
# TRANSFORM BMI VARIABLE 
health$bmi_trans <- health$bmi^(-1)
```



*Table 1: CHIS 2021 Data*
```{r, echo= FALSE, message=FALSE, warning=FALSE}
# FINAL DATA 
library(DT)
datatable(health, caption = htmltools::tags$caption(
                  style = ' caption-side: top;text-align: left;  font-size: 16px; font-style:italic;',
                  'Table 1: CHIS 2021 Data'), selection="multiple", rownames = FALSE,filter="top", options = list(pageLength = 5, 
                  lengthChange = FALSE, scrollX=F, fixedColumns = FALSE, sDom  = '<"top">lrt<"bottom">ip', 
                  columnDefs = list(list(width = '40px', targets = "_all"))))
```

# II. Exploratory Data Analysis 

*Table 2: Data summary*
```{r,  echo=FALSE,results = "asis",fig.caption = 'Table 2: Data summary', fig.align = 'center', out.width="50%",message=FALSE, warning=FALSE}
# DATAFRAME SUMMARY 
library(summarytools)
print(dfSummary(health, plain.ascii  = TRUE,  headings     = FALSE,
          style        = "multiline", 
          graph.col    = FALSE, 
          valid.col    = FALSE, silent = TRUE, varnumbers = FALSE, display.labels = TRUE, footnote = ''), method = 'pander',headings = FALSE, bootstrap.css = FALSE)
```

*Table 3: Descriptive statistics*
```{r,  echo=FALSE,results = "asis",fig.align = 'center', message=FALSE, warning=FALSE}
# SUMMARY OF QUANTITATIVE FEATURES  
print(descr(health, headings     = FALSE,style = "rmarkdown"), method = 'pander')
```

```{r,  echo=FALSE,results = "asis", fig.align = 'center', message=FALSE, warning=FALSE}
# AVERAGE BMI OF OBESE SUBJECTS 
library("dplyr")    
health %>%                              
  group_by(obese) %>% 
  summarize(min = min(bmi),
            q1 = quantile(bmi, 0.25),
            median = median(bmi),
            mean = mean(bmi),
            q3 = quantile(bmi, 0.75),
            max = max(bmi))
```

*Table 4: Cross-Tabulations*
```{r,  echo=FALSE,results = "asis", fig.align = 'center', message=FALSE, warning=FALSE}
# CROSS-TABULATION: OBESITY + INSURANCE 
with(health, 
     print(ctable(x = insurance, 
                  y = obese, 
                  prop     = 'n',
                  chisq = TRUE,
                   OR    = TRUE,
                   RR    = TRUE,
                  totals   = FALSE, 
                  headings = FALSE),
           method = "pander")
)
```

```{r,  echo=FALSE,results = "asis", fig.align = 'center', message=FALSE, warning=FALSE}
# CROSS-TABULATION: EMPLOYMENT + INSURANCE 
with(health, 
     print(ctable(x = insurance, 
                  y = employment, 
                  prop     = 'n',
                  chisq = TRUE,
                   OR    = TRUE,
                   RR    = TRUE,
                  totals   = FALSE, 
                  headings = FALSE),
           method = "pander")
)
```

```{r,  echo=FALSE,results = "asis", fig.align = 'center', message=FALSE, warning=FALSE}
# CROSS-TABULATION: OBESITY + EMPLOYMENT 
with(health, 
     print(ctable(x = obese, 
                  y = employment, 
                  prop     = 'n',
                  chisq = TRUE,
                   OR    = TRUE,
                   RR    = TRUE,
                  totals   = FALSE, 
                  headings = FALSE),
           method = "pander")
)
```

```{r,  echo=FALSE, fig.caption = 'Table 2: Data summary', fig.align = 'center', message=FALSE, warning=FALSE}
# BOXPLOT 
library(ggplot2)
library(plotly)
fig <- plot_ly(health, x = ~insurance, y = ~bmi, color = ~employment, type = "box")
fig <- fig %>% layout(boxmode = "group")
fig <- fig %>% layout(title = "")
fig
```

```{r,  echo=FALSE, fig.align = 'center', message=FALSE, warning=FALSE}
# ASSESS NORMALITY OF CONT OUTCOME BMI  
f2 <- ggplot(health, aes(x = bmi)) + 
    geom_histogram(aes(y = ..density..),bins = 30, fill = "#69b3a2", color = "white",alpha=0.8) +
                labs(x="bmi")

f4 <- ggplot(health, aes(x = log(bmi))) +
    geom_histogram(aes(y = ..density..),bins = 30, fill = "#69b3a2", color = "white",alpha=0.8) +
                labs(x="log(bmi)")

f5<- ggplot(health, aes(x = (bmi)^(-1))) +
    geom_histogram(aes(y = ..density..),bins = 30, fill = "#69b3a2", color = "white",alpha=0.8) +
                labs(x="bmi^(-1)")

plotly::subplot(f2, f4, f5, nrows=1, shareX=F, shareY=F, margin =0.02,titleX = TRUE)
```



```{r,  echo=FALSE, fig.align = 'center', message=FALSE, warning=FALSE}
# BAR PLOT OF FEATURES 
f2 <- ggplot(health, aes(y = age)) + 
    geom_bar( fill = "#69b3a2", color = "white",alpha=0.8) +
                labs(x="age")

f4 <- ggplot(health, aes(y = gender)) +
     geom_bar( fill = "#69b3a2", color = "white",alpha=0.8)  +
                labs(x="gender")

f5<- ggplot(health, aes(y = race)) +
     geom_bar( fill = "#69b3a2", color = "white",alpha=0.8) +
                labs(x="race")

f6<- ggplot(health, aes(y = family_size)) +
     geom_bar( fill = "#69b3a2", color = "white",alpha=0.8) +
                labs(x="family_size")

f7<- ggplot(health, aes(y  = education)) +
     geom_bar( fill = "#69b3a2", color = "white",alpha=0.8) +
                labs(x="education")
f8<- ggplot(health, aes(y = hhtotal_income)) +
     geom_bar( fill = "#69b3a2", color = "white",alpha=0.8) +
                labs(x="hhtotal_income")
f9<- ggplot(health, aes(y  = percent_life_US)) +
     geom_bar( fill = "#69b3a2", color = "white",alpha=0.8) +
                labs(x="percent_life_US")
f10<- ggplot(health, aes(y  = gen_health_cond)) +
     geom_bar( fill = "#69b3a2", color = "white",alpha=0.8) +
                labs(x="gen_health_cond")

plotly::subplot(f2, f4, f5,f6, f7, f8, f9, f10,  nrows=4, shareX=F, shareY=F, margin =0.08,titleX = TRUE)
```


# III. Instrumental Variables 

```{r,  echo=FALSE, fig.align = 'center', message=FALSE, warning=FALSE}
# NONPARAMETRIC CHI-SQUARE TEST: ASSOCIATION BETW CAT VARS 
library(janitor)
chisq.test(health %>% tabyl(insurance, employment ))
chisq.test(health %>% tabyl(insurance, family_size ))
chisq.test(health %>% tabyl(insurance, education ))
chisq.test(health %>% tabyl(insurance, hhtotal_income ))
chisq.test(health %>% tabyl(insurance, citizenship ))
chisq.test(health %>% tabyl(insurance, percent_life_US ))
chisq.test(health %>% tabyl(insurance, gen_health_cond ))
chisq.test(health %>% tabyl(obese, gen_health_cond ))
chisq.test(health %>% tabyl(age, employment ))
chisq.test(health %>% tabyl(race, employment ))
chisq.test(health %>% tabyl(race, age ))
```



```{r,  echo=FALSE, fig.align = 'center', message=FALSE, warning=FALSE}
# NONPARAMETRIC KRUSAL WALLIS TEST: ASSOCIATION BETW CAT AND CONT VARS 
library(stats)
kruskal.test(bmi~employment, data = health)
kruskal.test(bmi~family_size, data = health)
kruskal.test(bmi ~ education, data = health)
kruskal.test(bmi ~ hhtotal_income, data = health)
kruskal.test(bmi ~ citizenship, data = health)
kruskal.test(bmi ~ percent_life_US, data = health)
kruskal.test(bmi ~ gen_health_cond, data = health)
```




```{r,  echo=FALSE, fig.align = 'center', message=FALSE, warning=FALSE}
# ANOVA
fit <- aov(bmi~insurance, data = health) 
summary(fit)
fit <- aov(bmi~employment, data = health) 
summary(fit)
fit <- aov(bmi~family_size, data = health) 
summary(fit)
fit <- aov(bmi~education, data = health) 
summary(fit)
fit <- aov(bmi~hhtotal_income, data = health) 
summary(fit)
fit <- aov(bmi~citizenship, data = health) 
summary(fit)
fit <- aov(bmi~percent_life_US, data = health) 
summary(fit)
fit <- aov(bmi~gen_health_cond, data = health) 
summary(fit)
```







```{r,  include=FALSE, message=FALSE, warning=FALSE}
# IV METHOD DIAGRAM
pacman::p_load(
  DiagrammeR,     # for flow diagrams
  networkD3,      # For alluvial/Sankey diagrams
  tidyverse)      # data management and visualization
```

```{r,  echo=FALSE, fig.align = 'center', fig.cap = 'Figure 11: OLS Model Diagnostic Plots',message=FALSE, warning=FALSE}
# IV METHOD DIAGRAM
library(DiagrammeR)
DiagrammeR::grViz("digraph surveillance_diagram{
         
                     graph[layout = dot, rankdir = LR, fontsize = 5, overlap = false, bgcolor=white]
                     
                     node[shape = circle, style = filled, width = 1.3]  
                     A[label = 'Employment \n (IV)', fillcolor = darkgrey, fontcolor = white]
                     B[label = 'Health Insurance \n (Treatment)', fillcolor = darkgrey, fontcolor = white]
                     C[label = 'BMI \n (Outcome)', fillcolor = darkgrey, fontcolor = white]
                     D[label = 'Unobserved \n Confounders', fillcolor = white, fontcolor = black]
                     
                    { rank=same A B C }
 
                     edge[color = black]
                     A -> B [headlabel = 'Relevance  ',color=darkgreen, fontcolor= darkgreen] 
                     B -> C [color=darkgreen] 
                     D -> C [color = blue]
                     D -> B [color = blue]
                     A -> C [label = '        Exclusion', color = red,style = dashed, fontcolor= red]
                     A -> D [label = '  Exogeneity', color = red,style = dashed, fontcolor= red]
                       
                     
                     }")
# tmp = DiagrammeRsvg::export_svg(tmp)
# tmp = charToRaw(tmp) # flatten
# rsvg::rsvg_png(tmp, "dag.png") # saved graph as png in current working directory
```





```{r table2.3.1, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
tabl <- "

| Variable                     | Treatment (Insurance Coverage)*      | Outcome (BMI)**            | Outcome (BMI)***           |
|------------------------------|--------------------------------------|----------------------------|----------------------------|
| employment                   | p-value < 2.2e-16                    | p-value = 0.6951           | p-value = 0.275            |
| family_size                  | p-value < 2.2e-16                    | p-value = 0.003808         | p-value = 0.00471          |
| education                    | p-value < 2.2e-16                    | p-value < 2.2e-16          | p-value < 2.2e-16          |
| hhtotal_income               | p-value < 2.2e-16                    | p-value < 2.2e-16          | p-value < 2.2e-16          |
| citizenship                  | p-value = 0.001534                   | p-value < 2.2e-16          | p-value < 2.2e-16          |
| percent_life_US              | p-value < 2.2e-16                    | p-value < 2.2e-16          | p-value < 2.2e-16          |
| gen_health_cond              | p-value < 2.2e-16                    | p-value < 2.2e-16          | p-value < 2.2e-16          |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```
`Table`: Proposed IVs (* = Chi-square test, ** = Kruskal-wallis test, ***= ANOVA)




# IV. Inferential Analysis**

## 1. Preliminary fitting 

```{r,  echo=FALSE, fig.align = 'center', message=FALSE, warning=FALSE}
# FULL MODEL WITH ALL CONTROL VARIABLES AND ORIGINAL RESPONSE 
pre_fit<- lm(bmi~ insurance + age + race + gender + family_size + 
    education + hhtotal_income + citizenship + percent_life_US + 
    gen_health_cond , data = health)
```

```{r,  echo=FALSE, fig.align = 'center', message=FALSE, warning=FALSE}
# FULL MODEL WITH ALL CONTROL VARIABLES AND TRANSFORMED RESPONSE 
full_model <- lm(bmi_trans ~ insurance + age + race + gender + family_size + 
    education + hhtotal_income + citizenship + percent_life_US + 
    gen_health_cond , data = health)

model_red <- lm(bmi_trans~1, data=health)
```



```{r,  echo=FALSE, fig.align = 'center', message=FALSE, warning=FALSE}
# BEST MODEL USING AIC 
library(MASS) #k=2 is AIC, k=log(n) is BIC
#trace = 0 to hide all steps output 
step_fs1<-stepAIC(model_red,scope=list(upper=full_model, lower=~1), trace = 0, direction="both", k=2)
step_fs1$anova
```

```{r,  echo=FALSE, fig.align = 'center', message=FALSE, warning=FALSE}
# BEST MODEL USING FORWARD STEPWISE 
step_fs2<-stepAIC(model_red,scope=list(upper=full_model, lower=~1), trace=0, direction="forward",k=2)
step_fs2$anova
```



```{r,  echo=FALSE, fig.align = 'center', message=FALSE, warning=FALSE}
# TEST WHETHER CITIZENSHIP SHOULD BE INCLUDED TO CONFIRM RESULTS ABOVE 
mod1 <- lm(bmi_trans ~ insurance+age+ race+ gender+ family_size+ education+ hhtotal_income+percent_life_US + 
    gen_health_cond + citizenship, data= health) 
mod2 <- lm(bmi_trans ~ insurance+age+ race+ gender+ family_size+ education+ hhtotal_income+ percent_life_US + 
    gen_health_cond, data= health) 
anova(mod1, mod2, test="LRT") 
```

```{r,  echo=FALSE, fig.align = 'center', message=FALSE, warning=FALSE}
# ANOVA TEST FOR EMPLOYMENT 
mod1 <- lm(bmi_trans ~ insurance+age+ race+ gender+ family_size+ education+ hhtotal_income+percent_life_US + 
    gen_health_cond, data= health) 
mod2 <- lm(bmi_trans ~ insurance+age+ race+ gender+ family_size+ education+ hhtotal_income+ percent_life_US + 
    gen_health_cond + employment, data= health) 
anova(mod1, mod2, test="LRT") 
```

```{r,  echo=FALSE, fig.align = 'center', message=FALSE, warning=FALSE}
# HETEROSCEDASTICITY-ROBUST F TEST USING WALD TEST
library(lmtest)
library(sandwich)
waldtest(mod1, mod2, vcov = vcovHC(mod2, type = "HC1"))
```

```{r, echo = FALSE,  fig.align = 'left', fig.cap = 'Figure 11: OLS Model Box-Cox Plot',message=FALSE, warning=FALSE}
# Box-cox
par(mfrow=c(1,2))
MASS::boxcox(pre_fit)
MASS::boxcox(full_model)
```


```{r,  echo=FALSE, fig.align = 'center', message=FALSE, warning=FALSE}
# FIT ANOVA 
fit_aov <- aov(bmi_trans~ insurance + age + race + gender + family_size + education + hhtotal_income  +citizenship  + percent_life_US + gen_health_cond , data = health)
summary(fit_aov)
```

## 2. OLS 

```{r,  echo=FALSE, fig.align = 'center', message=FALSE, warning=FALSE}
# FIT MULTIVARIATE LINEAR REGRESSION OF TRANSFORMED BMI 
fit_ols <- lm(bmi_trans~ insurance+ age + race + gender + family_size + education + hhtotal_income  
                        + percent_life_US +  gen_health_cond, data = health)
summary(fit_ols)
```




## 3. 2SLS (Manual)

```{r, echo = FALSE,  fig.align = 'left', fig.cap = 'Figure 11: Box-Cox Plot',message=FALSE, warning=FALSE}
# STAGE 1 OLS (same result as bove)
X <- model.matrix(~  insurance, data = health)
Z <- model.matrix(~ age + race + gender + family_size + education + hhtotal_income  
                        + percent_life_US +  gen_health_cond + employment, data = health)
stage_1 <- lm(X ~ Z)
print(summary(stage_1)[2])
```

```{r, echo = FALSE,  fig.align = 'left', fig.cap = 'Figure 11: Box-Cox Plot',message=FALSE, warning=FALSE}
# STAGE 1 OLS W/ CONTROL VARIABLES TREATED AS BOTH INDEPENDENT AND INSTRUMENTAL VARIABLES 
X <- model.matrix(~  insurance+ age + race + gender + family_size + education + hhtotal_income  
                        + percent_life_US +  gen_health_cond , data = health)
Z <- model.matrix(~ age + race + gender + family_size + education + hhtotal_income  
                        + percent_life_US +  gen_health_cond + employment, data = health)
stage_1 <- lm(X ~ Z)
print(summary(stage_1,  vcov = vcovHC(fit_ivreg, type = "HC1"))[2])
```


```{r, echo = FALSE,  fig.align = 'left', fig.cap = 'Figure 11: Box-Cox Plot',message=FALSE, warning=FALSE}
# STAGE 2 OLS 
X_hat <- fitted(stage_1)
stage_2 <- lm(health$bmi_trans ~ X_hat)
# USE  HETEROSCEDASTICITY-ROBUST (HC) VAR-COV ESTIMATOR TO COMPUTE SE OF EST. COEFFS
summary(stage_2, vcov = vcovHC(fit_ivreg, type = "HC1"))
```

Reference: [Source](http://bkenkel.com/psci8357/notes/10-2sls.pdf)


## 4. 2SLS (ivreg)


```{r, echo = FALSE,  fig.align = 'left', fig.cap = 'Figure 11: Box-Cox Plot',message=FALSE, warning=FALSE}
# MULTIVARIATE 2SLS OF 1/BMI ON INSURANCE AND OTHERS WITH EMPLOYMENT AS THE IV 
library(AER) 
fit_ivreg <- ivreg(bmi_trans~insurance+ age + race + gender + family_size + education + hhtotal_income  
                        + percent_life_US +  gen_health_cond | age + race + gender + family_size + education 
                        +  hhtotal_income + percent_life_US +  gen_health_cond  + employment ,data=health)
summary(fit_ivreg,diagnostics = TRUE)
```

```{r, echo = FALSE,  fig.align = 'left', fig.cap = 'Figure 11: Box-Cox Plot',message=FALSE, warning=FALSE}
# USE SANDWICH ESTIMATOR TO COMPUTE VAR-COV MATRIX OF EST. COEFFS 
summary(fit_ivreg, vcov = sandwich, diagnostics = TRUE)
```

```{r, echo = FALSE,  fig.align = 'left', fig.cap = 'Figure 11: Box-Cox Plot',message=FALSE, warning=FALSE}
# USE  HETEROSCEDASTICITY-ROBUST (HC) VAR-COV ESTIMATOR TO COMPUTE SE OF EST. COEFFS
summary(fit_ivreg,vcov = vcovHC(fit_ivreg, type = "HC1"), diagnostics = TRUE)
```



```{r, echo = FALSE,  fig.align = 'left', fig.cap = 'Figure 11: Box-Cox Plot',message=FALSE, warning=FALSE}
# t-TEST OF COEFFICIENTS 
library(lmtest)
coeftest(fit_ivreg, vcov = vcovHC, type = "HC1")
```



# V. Sensitivity Analysis

```{r, echo = FALSE,  fig.align = 'left', fig.cap = 'Figure 11: Box-Cox Plot',message=FALSE, warning=FALSE}
# COMPARE ESTIMATES AND S.E. BETW. OLS AND IV REGRESSION  
car::compareCoefs(fit_ols, fit_ivreg)
```


```{r, echo = FALSE,  fig.align = 'left', fig.cap = 'Figure 11: Box-Cox Plot',message=FALSE, warning=FALSE}
# OLS VS. IV REGRESSION 
library("modelsummary")
m_list <- list(OLS = fit_ols, IV = fit_ivreg)
msummary(m_list)
```

```{r, echo = FALSE,  fig.align = 'left', fig.cap = 'Figure 11: Box-Cox Plot',message=FALSE, warning=FALSE}
# PLOT OLS VS. IV REGRESSION EST. COEFFICIENTS 
modelplot(m_list, coef_omit = "Intercept|experience")
```


```{r,  echo=FALSE, fig.align = 'center', fig.cap = 'Figure 11: OLS Model Diagnostic Plots',message=FALSE, warning=FALSE}
# MODEL DIAGNOSTIC PLOTS: OLS  
par(mfrow=c(2,2))
plot(pre_fit,pch =20, cex = 2, col = "aquamarine2")
```



```{r,  echo=FALSE, fig.align = 'center', fig.cap = 'Figure 11: OLS Model Diagnostic Plots',message=FALSE, warning=FALSE}
# MODEL DIAGNOSTIC PLOTS: OLS  
par(mfrow=c(2,2))
plot(fit_ols,pch =20, cex = 2, col = "aquamarine2")
```

```{r,  echo=FALSE, fig.align = 'center', fig.cap = 'Figure 11: OLS Model Diagnostic Plots',message=FALSE, warning=FALSE}
# MODEL DIAGNOSTIC PLOTS: 2SLS
par(mfrow=c(2,2))
plot(stage_2,pch =20, cex = 2, col = "aquamarine2")
```



```{r, echo = FALSE,  fig.align = 'left', fig.cap = 'Figure 11: Box-Cox Plot',message=FALSE, warning=FALSE}
# WALD TEST
library(lmtest)
wald_test <- waldtest(fit_ivreg)
print(wald_test)
```

## Using `ivmodel` to implement 2SLS 

```{r echo=FALSE, fig.align='left', fig.cap='Figure 11: Box-Cox Plot', message=FALSE, warning=FALSE}
# ANDERSON-RUBIN TEST
library(ivmodel)
library(dplyr)
Y=health$bmi_trans
d <- recode(health$insurance, 'Public' = 1, 'Private' = 0) #recode treatment 
#D=health$insurance
Z=health$employment
X_name=c('age' ,'race' , 'gender' , 'family_size' ,'education' , 'hhtotal_income' ,'percent_life_US' ,  'gen_health_cond')
X=health[X_name]
fit_ivmodel = ivmodel(Y=Y,D=d,Z=Z,X=X)
fit_ivmodel
```
```{r echo=FALSE, fig.align='left', fig.cap='Figure 11: Box-Cox Plot', message=FALSE, warning=FALSE}
# AR TEST
AR.test(fit_ivmodel, beta0 = 0, alpha = 0.05)
```

```{r echo=FALSE, fig.align='left', fig.cap='Figure 11: Box-Cox Plot', message=FALSE, warning=FALSE}
confint(fit_ivmodel)
```

```{r echo=FALSE, fig.align='left', fig.cap='Figure 11: Box-Cox Plot', message=FALSE, warning=FALSE}
IVpower(fit_ivmodel, beta=0.05)
IVpower(fit_ivmodel, type="AR",beta=0.1)
```


```{r echo=FALSE, fig.align='left', fig.cap='Figure 11: Box-Cox Plot', message=FALSE, warning=FALSE}
# MIN SIZE NEEDED TO ACHIEVE A SPECIFIC POWER THRESHOLD
IVsize(fit_ivmodel, beta=0.1,power=0.8)
IVsize(fit_ivmodel, beta=0.1,power=0.8, type="AR")
```












